### 2017-05-01 paper/paper.tex
Added formula for problem 2.

\part{基于SSA算法的含噪声时间序列预测}
\section{时间序列的分解}

\section{与其他方法的比较分析}
\section{对方案可靠性的评估}
\section{不同突变点原因分析}

>>>>

\part{基于SSA算法的含噪声时间序列预测}
\section*{Symbols}
\begin{table}[H]
	\centering
	\caption{}
	\label{tab:ssa_symbols}
	\begin{tabular}{ccc}
		\hline
		符号 & 含义 & 备注 \\
		\hline
		$L$ & windows length & \\
		$N$ & the sample numbers & \\
		$f_i$ & the value of f at time i & $f \in \{B, S, R\}$ \\
		$\textbf{X}$ & trajectory matrix & \\
		$d$ & number of non-zero characters & \\
		$r$ & number of primary singular values & \\
		$a_i$ & coeffiencients of LRF & \\
		\hline
	\end{tabular} \\
\end{table}
\section{时间序列的分解}
\subsection{Trajectory}
\begin{equation}
	\label{eqn:F_i}
	F_i = (f_{i-1}, \cdots, f_{i+L-2})^T  (1 \leq i \leq K = N - L + 1)
\end{equation}

\begin{equation}
	\label{eqn:X}
	\textbf{X} = (F_1, \cdots, F_K)
\end{equation}

\subsection{SVD}

\begin{equation}
	\label{eqn:S}
	S = \textbf{X} \textbf{X}^T
\end{equation}

$S$ has characters $\lambda_i$ and according character vector $U_i$

\begin{equation}
	\label{eqn:V_i}
	V_i = \textbf{X}^T U_i / \sqrt{\lambda_i}
\end{equation}

\begin{equation}
	\label{eqn:X_i}
	\textbf{$X_i$} = \sqrt{\lambda_i} U_i V_i^T
\end{equation}

\begin{equation}
	\label{eqn:SVD_expanded}
	\textbf{X} = \Sigma_{i=1}^d \textbf{$X_i$}
\end{equation}
where
\begin{equation}
	\label{eqn:non-zero-char-d}
	d = max\{i \textbar \lambda_i > 0\}
\end{equation}
and we choose $r$ to be less than $d$.

\subsection{Reconstruction}
based on \ref{eqn:SVD_expanded} we can define
\begin{equation}
	\label{eqn:SVD}
	\textbf{X} = \textbf{U} \Sigma \textbf{V}^T
\end{equation}
where
\begin{equation}
	\label{eqn:SVD_U}
	\textbf{U} = (U_1, \cdots, U_K)
\end{equation}
\begin{equation}
	\label{eqn:SVD_Sigma}
	\Sigma = diag(\sqrt{\lambda_1}, \cdots, \sqrt{\lambda_K})
\end{equation}
\begin{equation}
	\label{eqn:SVD_V} 
	\textbf{V} = (V_1, \cdots, V_L)
\end{equation}

def of $a_i$
\begin{align}
	\textrm{R} &= (a_{L-1}, \cdots, a_1)^T \\
	           &= \frac{1}{1-\nu^2} \Sigma_{i=1}^r \pi_i U_i^\nabla \label{eqn:R_a}
\end{align}
where $\pi_i$ is the last component of the vector $U_i$, $U_i^\nabla$ is exactly $U_i$ but for the last component, and
\begin{equation}
	\label{eqn:ssa_nu^2}
	\nu^2 = \Sigma_{i=1}^r \pi_i^2
\end{equation}

\subsection{prediction}
as simple as
\begin{equation}
	\label{eqn:ssa_prediction}
	\tilde{f}_N = \Sigma_{i=1}^{L-1} a_i \cdot f_{N-L+i} 
\end{equation}

Add $\tilde{f}_N$ to $F$, we get
\begin{equation}
	\label{eqn:ssa_new_f}
	\tilde{F} = (f_0, \cdots, f_{N-1}, \tilde{f}_N)
\end{equation}
use $\tilde{F}$ to generate $\tilde{X}$, and finally iterate.
\section{与其他方法的比较分析}
\section{对方案可靠性的评估}
\section{不同突变点原因分析}
